\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{\articletitle}

### 2015-04-07 paper/paper.tex
Start of results

% Python code
\usepackage{listings}
\lstset{
numbers=left,
breaklines=true
}

@@

% Bibliography
\usepackage[backend=bibtex, sorting=none]{biblatex}
\bibliography{references.bib}

@@

For this paper, the time complexity of the algorithms will be calculated. The difference in performance between the cases will be shown by computational results as well as the calculated time complexities.

@@

\subsection{Experiment Setup}
For the testing, a single laptop was used to collect all the timed data. The tests were run in JetBrains' PyCharm, using the built-in functions to run the python code. The python interpreter used was Python 3.4 and the laptop was running Windows 8.1 at the time of the testing. Efforts were made to ensure all the testing was performed under the same circumstances.

@@

For every chosen test instance, the run times for both algorithms was determined. After all testing all instances had been completed, the results were compared.
\\ \\
\textbf{\emph{TODO:} possibly rewrite the testing process after the testing; make sure timer details are correct}

%------------------------------------------------
\section{Description of Algorithms}
For hard instances of the graph isomorphism problem, the coarsest stable coloring of a graph still has a lot of colors which are not unique. Two structures for which this is the case are twins and false twins, they are defined in definition \ref{deftwins} and \ref{deffalsetwins}.
\begin{definition}
Let $G = (V,E)$ be a graph. The \emph{neighbourhood} $N(v)$ of $v \in V$ is:
$N(v) = \left\{{u \in V : \{u,v\} \in E}\right\}$
\end{definition}
\begin{definition}\label{deftwins}
Let $G = (V,E)$ be a graph.
Two vertices $u, v \in V$ are \emph{twins} if $\{u,v\} \in E$ and $N(u)\textbackslash {v} = N(v)\textbackslash {u}$.
\end{definition}
\begin{definition}\label{deffalsetwins}
Let $G = (V,E)$ be a graph.
Two vertices $u, v \in V(G)$ are \emph{false twins} if $N(u) = N(v).$
\end{definition}

To solve the graph isomorphism problem more efficiently, we use preprocessing algorithms which replaces twins and false twins by single precolored vertices such that:
\begin{compactenum}
\item Twins have the same color $\iff$ Twins have the same size (number of vertices).
\item False twins have the same color $\iff$ False twins have the same size (number of vertices).
\item A twin and a false twin can't have the same color.
\end{compactenum}

\subsection{Implementation}
The algorithm is divided into two subalgorithms. The subalgorithm \textit{gettwins} finds all twins and false twins and the subalgorithm \textit{preprocessing} replaces each (false) twin by a single colored vertex as described above. In the following subsections these algorithms and their worst case time complexities will be analyzed. The elementary operation is the comparison of two elements. In those subsections $n$ is the number of vertices of a graph $G(V,E)$ and $m$ is the number of edges of that graph.

\subsubsection{Finding twins and false twins}
The algorithm \emph{gettwins} can be found in appendix \ref{gettwins}. In line 2-10 two lists, \emph{nbs} and \emph{nbs2}, are created. Both lists contains $n$ sorted sublists. In the former list each sublist contains all the neighbours of a node and in the latter each sublist contains all the neighbours of a node and also the node itself. Finding all the neighbours only require going though all the edges once, so the time complexity is $O(m)$. The sorting algorithm has time complexity $O(n \log n)$, but since it's in a for loop of length $n$ the overall time complexity becomes $O(n^2 \log n)$.

In line 11-16 a dictionary \emph{falsetwins} is created where the keys are all the items from \emph{nbs} and the values a list of the corresponding vertices. Since \emph{nbs} has length $n$ and \emph{falsetwins} has at most length $n$, the time complexity of this is $O(n^2)$. In line 23 the items in the \emph{falsetwins} with only one vertex as value are removed. This is $O(n)$, since len() has $O(1)$.\cite{website:pythonTimeComplexity} The remaining values of the dictionary \emph{falsetwins} are now all the sets of false twins as defined in definition \ref{deffalsetwins}. A similar dictionary \emph{twins} is created where the keys are the items from \emph{nbs2}. The time complexity of \textit{gettwins} is thus $O(n^2 \log n)$.

@@

%------------------------------------------------
\section{Proof of Correctness}
NOG NIET AF!
\begin{definition}
A \emph{colored} graph $G(E,V)$ is a graph where each vertex $v \in V$ has a color label.
\end{definition}
\begin{definition}
Let $G_1 = (V_1, E_1)$ and $G_2 = (V_2, E_2)$ be two undirected colored graphs. A function $f: V_1 \to V_2$ is called a \emph{graph isomorphism} if (a) $f$ is a bijection, (b) for all $a, b \in V_1, \{a, b\} \in E_1$ if and only if $\{f(a), f(b)\} \in E_2$, and (c) $color(v)$ = $color (f(v)$. When such a function exist, $G_1$ and $G_2$ are called \emph{isomorphic graphs}. 
\end{definition}
\begin{theorem}
Let $G_1 = (V_1, E_1)$ and $G_2 = (V_2, E_2)$ be two undirected colored graphs where each vertex has the same color and let $H_1 = (V_1, E_1)$ and $H_2 = (V_2, E_2)$ be resp. the same graphs as $G_1$ and $G_2$ where each twin is replaced by a colored vertex such that (a) Each twin
\end{theorem}

@@

%------------------------------------------------
\section{Computational Experiments}

Computational Experiments here\\
Setup good experiments beforehand and test extensively

@@

Results here

@@

\section{Python code}
\lstset{language=Python}
\begin{lstlisting}[label={gettwins}]
def gettwins(g):
    nbs = []
    nbs2 = []
    for vertex in g.V():
        nb = vertex.nbs()[:]
        nb.sort(key=lambda x: x._label)
        nbs.append(tuple(nb))
        nb.append(vertex)
        nb.sort(key=lambda x: x._label)
        nbs2.append(tuple(nb))
    falsetwins = {}
    for i, item in enumerate(nbs):
        if item in falsetwins.keys():
            falsetwins[item].append(g.V()[i])
        else:
            falsetwins[item] = [g.V()[i]]
    twins = {}
    for i, item in enumerate(nbs2):
        if item in twins.keys():
            twins[item].append(g.V()[i])
        else:
            twins[item] = [g.V()[i]]
    falsetwins = {k: v for k, v in falsetwins.items() if len(v) > 1}
    twins = {k: v for k, v in twins.items() if len(v) > 1}
    return list(falsetwins.values()), list(twins.values()), list(falsetwins.keys()), list(twins.keys())   
\end{lstlisting}
\end{appendices}

\end{document}

>>>>

% Python code

\usepackage{listings}
\lstset{
numbers=left
}

@@

% Bibliography
\usepackage[backend=bibtex]{biblatex}
\bibliography{references.bib}

@@

For this paper, the time complexity of the algorithms will not be discussed or calculated. The difference in performance between the cases will be shown with a statistical analysis on computational results.

@@

\subsection{Experiment Setup}
For the testing, a single laptop was used to collect all the timed data. The tests were run in JetBrains' PyCharm, using the built-in functions to run the python code. The python interpreter used was Python 3.4 and the laptop was running Windows 8.1 @ 1.6 GHz/ 3.67GB RAM at the time of the testing. Efforts were made to ensure all the testing was performed under the same circumstances.

@@

For every chosen test instance, the run times for both algorithms was determined. After all testing all instances had been completed, the results were compared and tested...
\\ \\
\textbf{\emph{TODO:} possibly rewrite the testing process after the testing; make sure timer details are correct; what statistical tests are we using?}

%------------------------------------------------
\section{Description of Algorithms}
For hard instances of the graph isomorphism problem, the coarsest stable coloring of a graph still has a lot of colors which are not unique. Two structures for which this is the case are twins and false twins, they are defined in definition \ref{deftwins} and \ref{deffalsetwins}.
\begin{definition}
Let $G = (V,E)$ be a graph. The \textit{neighbourhood} $N(v)$ of $v \in V$ is:
$N(v) = \left\{{u \in V : \{u,v\} \in E}\right\}$
\end{definition}
\begin{definition}\label{deftwins}
Let $G = (V,E)$ be a graph.
Two vertices $u, v \in V$ are \textit{twins} if $\{u,v\} \in E$ and $N(u)\textbackslash {v} = N(v)\textbackslash {u}$.
\end{definition}
\begin{definition}\label{deffalsetwins}
Let $G = (V,E)$ be a graph.
Two vertices $u, v \in V(G)$ are \textit{false twins} if $N(u) = N(v).$
\end{definition}

To solve the graph isomorphism problem more efficiently, we use preprocessing algorithms which replaces twins and false twins by single precolored vertices such that:
\begin{enumerate}
\item Twins have the same color $\iff$ Twins have the same size (number of vertices).
\item False twins have the same color $\iff$ False twins have the same size (number of vertices).
\item A twin and a false twin can't have the same color.
\end{enumerate}
\subsection{Implementation}
The algorithm is divided into two subalgorithms. The subalgorithm \textit{gettwins} finds all twins and false twins and the subalgorithm \textit{preprocessing} replaces each (false) twin by a single colored vertex as described above. In the following subsections these algorithms and their worst case time complexities will be analyzed. The elementary operation is the comparison of two elements. In those subsections $n$ is the number of vertices of a graph $G(V,E)$ and $m$ is the number of edges of that graph.

\subsubsection{Finding twins and false twins}
The algorithm \textit{gettwins} can be found in appendix \ref{gettwins}. In line 2-10 two lists, \textit{nbs} and \textit{nbs2}, are created. Both lists contains $n$ sorted sublists. In the former list each sublist contains all the neighbours of a node and in the latter each sublist contains all the neighbours of a node and also the node itself. Finding all the neighbours only require going though all the edges once, so the time complexity is $O(m)$. The sorting algorithm has time complexity $O(n \log n)$, but since it's in a for loop of length $n$ the overall time complexity becomes $O(n^2 \log n)$. \\\newline In line 11-16 a dictionary \textit{falsetwins} is created where the keys are all the items from \textit{nbs} and the values a list of the corresponding vertices. Since \textit{nbs} has length $n$ and \textit{falsetwins} has at most length $n$, the time complexity of this is $O(n^2)$. In line 23 the items in the \textit{falsetwins} with only one vertex as value are removed. This is $O(n)$, since len() has $O(1)$. The remaining values of the dictionary \textit{falsetwins} are now all the sets of false twins as defined in definition \ref{deffalsetwins}. A similar dictionary \textit{twins} is created where the keys are the items from \textit{nbs2}. The time complexity of \textit{gettwins} is thus $O(n^2 \log n)$.
%BRON https://wiki.python.org/moin/TimeComplexity

@@

%------------------------------------------------
\section{Proof of Correctness}
NOG NIET AF!
\begin{definition}
A \textit{colored} graph $G(E,V)$ is a graph where each vertex $v \in V$ has a color label.
\end{definition}
\begin{definition}
Let $G_1 = (V_1, E_1)$ and $G_2 = (V_2, E_2)$ be two undirected colored graphs. A function $f: V_1 \to V_2$ is called a \textit{graph isomorphism} if (a) $f$ is a bijection, (b) for all $a, b \in V_1, \{a, b\} \in E_1$ if and only if $\{f(a), f(b)\} \in E_2$, and (c) $color(v)$ = $color (f(v)$. When such a function exist, $G_1$ and $G_2$ are called \textit{isomorphic graphs}. 
\end{definition}
\begin{theorem}
Let $G_1 = (V_1, E_1)$ and $G_2 = (V_2, E_2)$ be two undirected colored graphs where each vertex has the same color and let $H_1 = (V_1, E_1)$ and $H_2 = (V_2, E_2)$ be resp. the same graphs as $G_1$ and $G_2$ where each twin is replaced by a colored vertex such that (a) Each twin
\end{theorem}

@@

@@

Results here \\
And statistical analysis of the results

@@

\section{Python code}
\lstset{language=Python}
\begin{lstlisting}[label={gettwins}]
def gettwins(g):
    nbs = []
    nbs2 = []
    for vertex in g.V():
        nb = vertex.nbs()[:]
        nb.sort(key=lambda x: x._label)
        nbs.append(tuple(nb))
        nb.append(vertex)
        nb.sort(key=lambda x: x._label)
        nbs2.append(tuple(nb))
    falsetwins = {}
    for i, item in enumerate(nbs):
        if item in falsetwins.keys():
            falsetwins[item].append(g.V()[i])
        else:
            falsetwins[item] = [g.V()[i]]
    twins = {}
    for i, item in enumerate(nbs2):
        if item in twins.keys():
            twins[item].append(g.V()[i])
        else:
            twins[item] = [g.V()[i]]
    falsetwins = {k: v for k, v in falsetwins.items() if len(v) > 1}
    twins = {k: v for k, v in twins.items() if len(v) > 1}
    return list(falsetwins.values()), list(twins.values()), list(falsetwins.keys()), list(twins.keys())   
\end{lstlisting}

\section{Table with computation times}
\begin{tabular}{c|c|c}
Graph & Computation time (without preprocessing) & Computation time (with preprocessing) \\
\hline
cographs1 & 146.8098 sec & 0.0171 sec \\
hugecographs & >30 min & 662.5381 sec \\
cycles175 & 69.8579 & 70.8041 sec \\
bigtrees3 & -1 & -1\\
cubes6 & -1 & -1\\
products72 & -1 & -1\\
torus72 & -1 & -1\\

\end{tabular}
\end{appendices}

\end{document}
Status API Training Shop Blog About
© 2015 GitHub, Inc. Terms Privacy Security Contact
